\textit{MSF: Modulated Sub-graph Finder}

### 2018-02-26 MSF_Paper_FA.tex
Updated Network and descritpion

The connected modulated sub-graphs from 6hpi are shown in~(Fig.~2). The sub-graph shows different colors for the predefined  KEGG pathways and how they are connected to each other. The KEGG enrichment and visualization on the modulated sub-graph was done using StringApp~\cite{StringApp} in Cytoscape. The sub-graph shows RIG-like receptor signaling is connected to Toll-like receptor, which intern connects to MAPK signaling, JAK-STAT signalling, Cytokine-cytokine signaling, Chemokine receptor signaling and TNF signaling. These pathways could be seen further leading to WNT Signaling and P13K-Akt signaling.

From the other side the ECM receptor interaction is seen to lead to Focal adhesion which regulates the P13k-Akt signaling. Finally P13k-Akt signaling leads to FoxO signaling which eventually connects to cell cycle. TNF, P13k-Akt and FoxO signaling activates apoptosis and autophagy.

@@

To show the robustness and stability of our method, Poisson
distributed noise was added to the sample read counts. 
Then DGEA was carried out on the disturbed data with the
same parameters as for the native data, followed by analysis with
\texttt{MSF}. Using this criteria, the goal was to spot almost
identical modulated sub-graphs in the real and noisy data. This procedure was carried out 100 times and every time the genes from the sub-graphs identified from noisy data were compared to the sub-graphs identified from the native data. The robustness of \texttt{MSF} for the three time-points is shown in~(Fig.~2). For the last time-point (2dpi) 84\% genes of the sub-graphs from native data were retrieved, for 1dpi the robustness was about 79\%. The robustness was the lowest at 6hpi nearly 71\%, this could be due to that the infection merely started and the signal transdcution was weak as compared to the later time-points and over that Poisson distributed noise was added to the data.

@@

We thank all our colleagues who provided insight and expertise that greatly assisted the research and all reviewers for their constructive criticism. \newpage

@@

\begin{figure*}
	\centering
	\includegraphics[width=1.6\linewidth]{ModulatesSubPaths/MSFData/Ebola6H/Merged_Network}
	\caption{Modulated Sub-graph from 6hpi}
\end{figure*}

\begin{figure*}[p]
	\includegraphics[width=16cm]{Git/MSF_Paper/3Timepoints}
	\caption{Robustness analysis for three time-points of infection}
\end{figure*}

>>>>

 The connected modulated sub-graphs from 6hpi are shown in~(Fig.~2). The sub-graph shows different colors for the predefined KEGG pathways and how they are connected to each other. The KEGG enrichment and visualization on the modulated sub-graph was done using StringApp~\cite{StringApp} in Cytoscape. The sub-graph shows activation of IRF-dependent genes, including those for type I IFNs through Toll-like receptor signaling, exhibiting strong inflammatory response as shown by elevated levels of inflammatory cytokines and chemokines. NF-Kappa B activation is also mediated by Toll-like receptor. NF-Kappa B signaling is a key regulator of cytokine and chemokine expression. Toll-like receptor signaling further leads to  MAPK signaling, JAK-STAT signaling and TNF signaling. Sensor of cytosolic DNA which activates the IRF and NF-{kappa}B transcription factors,also leads to production of type I interferon and other cytokines.

 From the other side the ECM receptor interaction is seen to lead to Focal adhesion which regulates the P13k-Akt signaling. Finally P13k-Akt signaling opens to FoxO signaling which eventually connects to cell cycle, which at later time-point is disrupted. TNF signaling, P13k-Akt signaling and FoxO signaling activates apoptosis and autophagy.

@@

To show the robustness and stability of our method, Poisson distributed noise was added to the sample read counts. Then DGEA was carried out on the disturbed data with the same parameters as for the native data, followed by analysis with \texttt{MSF}. Using this criteria, the goal was to spot almost
identical modulated sub-graphs in the real and noisy data. This procedure was carried out 100 times and every time the genes from the sub-graphs identified from noisy data were compared to the sub-graphs identified from the native data. This was also done for the DEG obtained for each run, a cutoff was used to identify the same number of retrieved DEG as the native data.  The robustness of \texttt{MSF} and the DEG analysis for the three time-points are shown in~(Fig.~3). Since we were very stringent in adding noise to the counts, which could be seen by the DEG analysis robustness.
For the last time-point (48hpi) 84\% genes of the sub-graphs from native data were retrieved, for 24hpi robustness was about 79\%. Robustness was the lowest at 6hpi nearly 71\%, this could be due to that the infection merely started and the signal transdcution was weak as compared to the later time-points.

@@

We thank all our colleagues who provided insight and expertise that greatly assisted the research and all reviewers for their constructive criticism.

\subsection*{Supplementary Material}

\newpage

@@

\begin{figure*}
	\centering
	\includegraphics[width=1.6\linewidth]{ModulatesSubPaths/MSFData/Ebola6H/Merged6hNetwork}
	\caption{Modulated Sub-graph from 6hpi, showing KEGG predefined pathways colored.}
	\label{fig:merged6hnetwork}
\end{figure*}

\begin{figure*}[p]
	\includegraphics[width=16cm]{Documents/PhDThesis/MSFPaper/DEGvsMSF2}
	\caption{Robustness analysis for three time-points of infection}
	\label{fig:degvsmsf2}
\end{figure*}
